---
output: github_document
always_allow_html: yes
---




```{r, include=FALSE}
options("width"=101)
tmp <- devtools:::read_dcf("DESCRIPTION")
```

```{r, results='asis', echo=FALSE}
cat("#", tmp$Title)
```


<br><br>
**Status**


[![Travis-CI Build Status](https://travis-ci.org/petermeissner/diffrprojectswidget.svg?branch=master)](https://travis-ci.org/petermeissner/diffrprojectswidget)
[![codecov](https://codecov.io/gh/petermeissner/diffrprojectswidget/branch/master/graph/badge.svg)](https://codecov.io/gh/petermeissner/diffrprojectswidget/tree/master/R)
[![CRAN version](http://www.r-pkg.org/badges/version/diffrprojectswidget)](https://cran.r-project.org/package=diffrprojectswidget)



```{r, include=FALSE}
filelist.R   <- list.files("R", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.tests   <- list.files("tests", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.cpp <- list.files("src", recursive = TRUE, pattern="\\.cpp$", ignore.case = TRUE, full.names = TRUE)
lines.R      <- unlist(lapply(filelist.R, readLines))
lines.tests  <- unlist(lapply(filelist.tests, readLines))
lines.cpp    <- unlist(lapply(filelist.cpp, readLines))
length.R     <- 
  length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.R,  value = TRUE, invert = TRUE))
length.tests <- 
  length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.tests,  value = TRUE, invert = TRUE))
length.cpp   <- 
  length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.cpp,  value = TRUE, invert = TRUE))
```





*R code:* `r length.R`<br> 
*C++ code:* `r length.cpp`<br> 
*test code:* `r length.tests`


<br><br>
**Version**

```{r, results='asis', echo=FALSE}
cat(tmp$Version)
```

<br><br>
**Description**

```{r, results='asis', echo=FALSE}
cat(tmp$Description)
```


<br><br>
**Funding**

This software was created as part of the "Institutional Design in Western European Democracies" research project, funded by [DFG (Deutsche Forschungsgemeinschaft)](http://gepris.dfg.de/gepris/projekt/146229116), lead by [Ulrich Sieberer](https://scholar.google.com/citations?user=Q_ImhbkAAAAJ) and based at [University Konstanz](https://www.uni-konstanz.de/). 


<br><br>
**License**

```{r, results='asis', echo=FALSE}
cat(tmp$License, "<br>")
cat(as.character(eval(parse(text=tmp$Author))))
```



<br><br>
**Citation**


```{r, results='asis', echo=FALSE}
citation("diffrprojectswidget")
```


<br><br>
**BibTex for citing**

```{r, eval=FALSE}
toBibtex(citation("diffrprojectswidget"))
```


<br><br>
**Installation**

```{r, eval=FALSE}
devtools::install_github("petermeissner/stringb")
devtools::install_github("petermeissner/rtext")
devtools::install_github("petermeissner/diffrprojects")
devtools::install_github("petermeissner/diffrprojects")
```

... or, alternatively from my private R package repository ... 

```{r, eval=FALSE}
options( "repos" = 
  c(
    options("repos")$repos, 
    petermeissner="https://petermeissner.github.io/drat"
  ) 
)
install.packages("diffrprojectswidget")
```


<br><br>
**Example usage**


```{r, message=FALSE}

library(diffrprojects)
library(diffrprojectswidget)

dp <-
  diffrproject$new()$
  text_add(list(prometheus_late, prometheus_early))$
  text_link()$
  text_align( maxDist = 1 )

dp$text_code_regex(text=1, x="you", pattern="du|Du", val=TRUE)
dp$text_code_regex(text=1, x="me", pattern="ich|Ich", val=TRUE)

dp$text_code_regex(text=2, x="you", pattern="du|Du", val=TRUE)
dp$text_code_regex(text=2, x="me", pattern="ich|Ich", val=TRUE)

dp$alignment_code(1,1,"dongs", "muhaha")
dp$alignment_code(1,1,"dings", "check this out")

dp$debug()

dp_vis(dp, link=1)
dp_table(dp, 1)
```


    
